Model Finding for Recursive Functions in SMT

### 2016-04-10 ijcar2016/body.tex
Add back paragraph

%By default, \cvc uses techniques to minimize the number of literals it
%considers when constructing propositional satisfying assignments for
%formulas~\cite{relevancy2007}. However, we have found such techniques degrade
%performance for finite model finding on problems having recursive functions
%that are defined by cases. For this reason, we disable the techniques for
%problems produced from our translation.

>>>>

By default, \cvc uses techniques to minimize the number of literals it
considers when constructing propositional satisfying assignments for
formulas~\cite{relevancy2007}. However, we have found such techniques degrade
performance for finite model finding on problems having recursive functions
that are defined by cases. For this reason, we disable the techniques for
problems produced from our translation.
